---
title: "SaferActive Report 2: Scenarios"
author: Institute for Transport Studies
output: bookdown::html_vignette2
vignette: >
  %\VignetteIndexEntry{SaferActive Report 2: Scenarios}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: saferactive.bib
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(trafficalmr)
```

# Software development

Underlying our work is data science, which requires the development of code to ensure reproducible and scalable analysis.
We have progressed with the development of the `trafficalmr` package for reproducible road safety analysis, supporting the project and other projects on road safety.
We would like feedback from stakeholders: is it easy to use? what additional functionality would you like to see? The list of functions provided by the package can be found here: https://saferactive.github.io/trafficalmr/reference/index.html

# Temporal analysis


# Spatial analysis


# Analysis of data on traffic calming


# Scenario development


# Next steps



