---
title: "SaferActive Report 3"
author: Institute for Transport Studies
output:
  bookdown::html_vignette2:
    number_sections: true
    toc: true
vignette: >
  %\VignetteIndexEntry{SaferActive Report 3}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: saferactive.bib
pkgdown:
  as_is: true
  set_null_theme: false
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE
)
```

```{r setup}
library(trafficalmr)
```

# Introduction




# Risk models


## Assigning collision data to a spatial grid


## Assigning census-derived cycling data to a spatial grid   


## Modelling spatio-temporal change in cycling uptake based on count data


## Validation of cycling uptake model results


## Modelling spatio-temporal change in collision risk




# Scenarios of change


## Traffic calming measures


## 20 mph zones


## Protected cycleways


## Traffic reduction


## Roadspace reallocation


## Low Traffic Neighbourhoods




# Data visualisation




# Web development




# Next steps




# References
